Deciding to Disclose

### 2015-06-17 model_description.tex
Reducing the pagecount
Substantially.

\section{Model Description}
\label{app:model_description}

@@

\subsection{Agent Models}
\label{sub:the_agents}
%Outline basic structure, then specifics on each one.
%This should probably go lexic -> bayes payoff -> bayes -> CPT in order
% of complexity.
%suggest there are added shells of complexity
%		mention the info sharing because homophilly
%			related - the enhancement to the bayes/cpt agents is that they personalise, as much as anything.
%		properly explain dirichlet priors
% How about comparing the decision problem representation for the agent types?

While in principle a wide variety of agent models are possible, given that decision rules operate on essentially the same information, and produce the same outputs, we limit ourselves here to four. The simplest is a lexicographic rule (1), in the spirit of a \ac{FFH} \citep{Gigerenzer2004} which uses only information about payoffs given actions; this is followed by a Bayesian risk minimisation rule (2) using the same information; a second Bayesian risk rule (3) which uses information about the underlying lottery; and a two-stage \ac{CPT} \citep{Hau2008} agent (4) which is identical to 3, but uses the \ac{CPT} decision rule from \cite{Tversky1992}. Hence, each successive decision model adds a layer of sophistication to the problem representation while retaining the same input-output characteristics.

As noted in section \ref{sub:the_game}, agents have perfect recall, and midwives recognise women if they repeatedly encounter them. While agents recall perfectly and make use of the new information for retrospective updates, all four agent models make decisions `as-if' they were always facing a new \enquote{opponent}.

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogeneous beliefs about  women and assume to some extent that they are honest.
Women have heterogeneous beliefs, which correspond to experiencing \(k\) randomly chosen paths through the game, and following each path at least once.

\subsubsection{Lexicographic Heuristic}
\label{sub:lexico}

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified problem representation, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. Where there is no clear best action, but one or more is evidently worse, a choice must be made as to whether to discard the poorer action; in this case we have elected to retain it.
This approach requires minimal computation, and does not assume that \(u_{i}\) is static, or known.

Women resolve this by approximating the utility function, as a function \(f(s_{w}, \sigma)\) on their choice of signal and an unknown distribution $\sigma$, which maps to \(u_{w}\) - i.e. \(s_{w}\) is a choice between simple lotteries. The algorithm maintains a count, \(n\), of the number of occurrences of each outcome given the choice from \(s_{w}\).

Midwives solve a slightly different problem with more information, where \(s_{w}\) is known, and \(s_{m}\) is the lottery choice - \(f(s_{w}, s_{m},\sigma)\). This is resolved by maintaining a separate count for each signal (i.e. \(n_{s_{w},s_{m}}\)), and otherwise following the same algorithm, presented below.

\begin{algorithm}
\begin{algorithmic}
\State n=1, action=none
\While{action is none}
\State Calculate the nth most common outcome following each action.
\State Sort actions by the value of the nth most common outcome.
\If{clear winner} \State action = best \EndIf
\State n = n + 1
\EndWhile
\State \Return action
\end{algorithmic}
\caption{Lexicographic heuristic\label{alg:lexico}}
\end{algorithm}

As an example, take a light drinker who has played three rounds with a succession of particularly judgemental midwives, signalling honestly in two and claiming to be a moderate drinker in one. The most common outcome of the honest signal was a payoff of 10, which is clearly preferable to the 9 gained by claiming to be moderate. On that basis, they choose to signal honestly.

\subsubsection{Bayesian Payoff}

The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using the Bayes rule, and attempts to choose the action which minimises risk.

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed as a prior to represent these beliefs. The probability
density function takes the form -

\begin{equation}
D(\Theta|\alpha)=\frac{\Gamma(\sum_{i=1}^{k}\alpha_{i})}{\prod_{i=1}^{k}\Gamma(\alpha_{i})}\overset{k}{\underset{i=1}{\prod}\Theta_{i}^{\alpha_{i-1}}}
\end{equation}

where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the 
pseudo-count of prior observations for a pair \(i\).

The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff becomes
simply -

\begin{equation}
p(x=j|D,\alpha)=\frac{\alpha_{j}+n_{j}}{\sum_{j}(\alpha_{j}+n_{j})}\label{eq:posterior}
\end{equation}

Where \(n_{j}\) is simply the count of occurrences of signal-payoff pair \(j\), so
that the belief that a signal will lead to a payoff is the number
of times that pairing has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.
As before, midwives follow a similar pattern but maintain \(n_{s_{w}}\) independent counts of pairings between referral choice and payoff, updating their beliefs about the relationship between the choice to refer and payoff given the signal they have received.

Agents then choose the strategy $s_{i}$ to minimise risk $R_{i}$, which is simply defined as - 
\begin{equation}
R_{w}(s_{w}) = \sum_{x \in X} -xp(x | s_{w})
\end{equation}
\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{x \in X} -xp(x | s_{w}\wedge s_{m}),
\end{equation}

where $X$ is the set of payoffs the agent has observed to follow $s_{i}$.

If we take our light drinker from the lexicographic case, and assume that they began with an uninformative prior. The 6 possible signal-payoffs pairings are then \([(l,10),(m,10),(h,10),(m,9),(h,9),(h,8)]\), with \(\alpha_{i}=1\) for all \(i\). After playing the three rounds, \(n_{l,10}=2\), and \(n_{m,9}=1\).

The agent then evaluates \(R_{w}\) for each signal, e.g. for the light signal:

\begin{equation*}
\begin{align*}
X &= \{10\}\\
R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
R_{w}(l) &= -10(\frac{3}{3}) = -10
\end{align*}
\end{equation*}

and by the same method, \(R_{w}(m)=-9\frac{1}{3}\), and \(R_{w}(h)=-9\), concluding that signalling honestly is the best move.

\subsubsection{Bayesian Risk Minimisation}

The second Bayesian agent augments the reasoning of the simple payoff model, making the stronger assumption that the utility function is static, and known. Women maintain two sets of beliefs, corresponding respectively to \(p_{m}\), and the probability of referral given signal choice. This leads to the risk function, minimised with respect to \(s_{w}\) -

\begin{equation}
R_{w}(s_{w}, \theta_{w}) = \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(s_{w}, i, \theta_{w}, j)p(j)p(i | s_{w}),
\end{equation}

so that the risk of a signal is the sum of the products of all payoffs with the probabilities of their entailed midwife types and responses.

Midwives reasoning centres on determining the meaning of signals, since given the knowledge of what some signal \(s_{w}\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise the following risk function, minimised with respect to \(s_{m}\) -

\begin{equation}
R_{m}(s_{w}, s_{m}) = \sum_{i\in \Theta} -u_{m}(s_{w}, s_{m}, i)p(i | s_{w})
\end{equation}

Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\). Their prior beliefs remain uninformative, i.e. \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\). As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -

\begin{equation*}
\begin{align*}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
u_{w}(l, i, l, j) &= 10\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
&= -10
\end{align*}
\end{equation*}

and similarly for moderate (\(R_{w}(m,l)=-9\frac{1}{3}\)), and heavy (\(R_{w}(h,l)=-8\frac{1}{2}\)) signals, once again concluding that honesty is the better option.

\subsubsection{Descriptive Decision Theory}

The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans. While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{FoxCPT}. In this instance the Bayesian inference process fills the first stage role.

%Maybe cut this bit and make explanation richer?
Rather than the psychologically more interesting \ac{PT}, the \ac{CPT}
decision rule is used in this instance, because of the requirement
for women to evaluate the `prospects'\footnote{Where a prospect is a sequence of payoff-probability pairings in ascending order of payoff, associated with an action.} of more than two actions. \ac{CPT} uses transformed probabilities, underweighting
small probabilities, and overweighting large ones. This is intended to reflect the observed behaviour of humans, where sufficiently high likelihoods are treated as certain, and contrastingly low probabilities as impossible. The correct weighting function is subject to some debate, but here we have used that of \citet{Tversky1992}, which treats probabilities differently for gains (eqn \ref{eqn:cpt_p_pos}) and losses (eqn \ref{eqn:cpt_p_neg}) -

\begin{align}
w^{+}(p) & = \frac{p^{\gamma}}{(p^{\gamma}+(1-p)^{\gamma})^{\frac{1}{\gamma}}}\label{eqn:cpt_p_pos}\\
w^{-}(p) & = \frac{p^{\delta}}{(p^{\delta}+(1-p)^{\delta})^{\frac{1}{\delta}}}\label{eqn:cpt_p_neg},
\end{align}

where $p$ is the unweighted probability, and $\gamma$ and $\delta$
are the weights for gain and loss probabilities respectively. Along similar lines, the values of losses and gains are transformed to reflect a tendency to regard a loss as more significant than a gain  -

\begin{equation}
v(u_{i})=\begin{cases}
f(u_{i}),& \text{if}\, u_{i}>0\\
0,& \text{if}\, u_{i}=0\\
\lambda g(u_{i}),& \text{if}\, x<0
\end{cases},
\end{equation}

where,

\begin{equation}
f(u_{i})=\begin{cases}
u_{i}^{\alpha},& \text{if}\,\alpha>0\\
\ln(u_{i}),& \text{if}\,\alpha=0\\
1-(1+u_{i})^{\alpha},& \text{if}\,\alpha<0
\end{cases}
\end{equation}
\begin{equation}
g(u_{i})=\begin{cases}
-(-u_{i})^{\beta},& \text{if}\,\beta>0\\
-\ln(-u_{i}),& \text{if}\,\beta=0\\
(1-u_{i})^{\beta}-1,& \text{if}\,\beta<0
\end{cases},
\end{equation}

and $\alpha$, and $\beta$ are respectively the power of a gain,
and a loss, and \(\lambda\) is a multiplier giving the aversion to loss.

Finally, the transformed probabilities are used to construct decision weights, \(\pi^{+},\pi^{-}\) for losses and gains, where,

\begin{equation}
\pi_{n}^{+}=w^{+}(p_{n})
\end{equation}
\begin{equation}
\pi_{-m}^{-}=w^{-}(p_{-m})
\end{equation}
\begin{equation}
\pi_{i}^{+}=w^{+}(p_{i}+\ldots+p_{n}) - w^{+}(p_{i+1}+\ldots+p_{n}),0\leq i \leq n - 1
\end{equation}
\begin{equation}
\pi_{i}^{-}=w^{-}(p_{-m}+\ldots+p_{i}) - w^{-}(p_{-m}+\ldots+p_{i-1}),1-m\leq i \leq 0
\end{equation}

The \ac{CPT} value of a single outcome prospect \(f=(u_{i};p_{i})\), is $v(u_{i})\pi^{+}(p_{i})$
if $u_{i}\geq0$, and $v(u_{i})\pi^{-}(p_{i})$ otherwise. For any given action the \ac{CPT}
value, \(V\) is the sum of the value of the prospects of that action, as
in the Bayesian risk model, and the agent chooses the option which maximises this quantity.

Once again, we return to the light drinker example.  The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$. For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:qt_params}.

\begin{equation*}
\begin{align*}
\alpha &= 0.88\\
\gamma &= 0.61\\
p(l) &= \frac{1}{6}\\
p(m) &= \frac{1}{6}\\
p(h) &= \frac{2}{3}\\
p(r | l) &= \frac{1}{4}\\
p(n | l) &= \frac{3}{4}\\
u_{w}(l, i, l, j) &= 10\\
f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
f^{+}&=f,f^{-}=()\\
n &= 5\\
v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
v(u_{w}) &= 10^{0.88} = 7.59\\
\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(1) - w^{+}(\frac{23}{24})\\
&=0.19\\
\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
&= 0.17\\
\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
&= 0.04\\
\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
&= 0.09\\
\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
&= 0.09\\
\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
&= 0.42\\
V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
\end{align*}
\end{equation*}

And as before, following the same process for moderate, and heavy signals which yields respectively 7.14, and 6.22, the agent chooses the higher valued action and sends an honest signal.

>>>>

\section{Model Description}
\label{app:detail_model_description}

@@

### 2015-06-17 simulation_schedule.tex
Reducing the pagecount
Substantially.

In this section we provide psuedocode for a single simulation, which encompasses several games.

\begin{algorithm}
\begin{algorithmic}
\State $rounds \gets 1000, appointments \gets 12$
\State women \gets enqueue([], $w_{1},\ldots,w_{1000}$), midwives \gets [$m_{1},\ldots,m_{100}$]
\While{$rounds > 0$}
	\State players $\gets$ dequeue first 100 women
	\State referred $\gets$ []
	\State $i $\gets$ 1$
	\While{$i < 100$}
		\State woman $\gets$ players[i], midwife $\gets$ midwives[i]
		\State signal $\gets$ signal(woman)
		\State response $\gets$ respond(midwife)
		\State midwife's memory $\gets$ woman, signal, response
		\State woman's memory $\gets$ type(midwife), signal, response, $X_{w, s, r, type(woman), type(midwife)}$
		\State update woman's beliefs
		\If{$response = refer$}
			\State midwife's memory $\gets$ type(woman), $X_{m, s, r, type(woman)}$
			\State retrospectively update midwife's beliefs
			\State women $\gets$ enqueue(women, new woman)
			\State Add woman to referred
		\Else
			women $\gets$ enqueue(women, woman)
		\EndIf
	\EndWhile
	\For{woman in referred}
		\If{$random \lt p$}
			\For{player in women}

			\EndFor
		\EndIf
	\EndFor
\State $rounds \gets rounds - 1$
\EndWhile
\end{algorithmic}
\caption{Simulation schedule\label{alg:sim}}
\end{algorithm}

>>>>

In this section we give the step by step process for a single run of the disclosure game simulation.

\begin{itemize}
\item Generate 1000 women, and place them in a queue
\item Generate 100 midwives.
\item For each round of the game
\begin{itemize}
\item Take 100 women from the queue
\item Pair each one with a random midwife
\item For each pair
\begin{itemize}
\item Woman sends a signal
\item Midwife refers or not based on the signal
\item Woman is informed of their payoff, the midwife's type, and whether they are referred
\item If the woman is referred
\begin{itemize}
\item The midwife is informed of the woman's true type
\item The midwife retrospectively updates their beliefs using the true type, and memories of any games with this woman
\item The midwife is now eligible to share their memories of games with this woman
\end{itemize}
\end{itemize}
\item Women who have not been referred, or had their baby join the back of the queue
\item Generate new women to replace those referred, or delivered
\item Add new women to the back of the queue
\item For each referred or birthed woman
\begin{itemize}
\item With probability p, their memory of games is shared with the active women
\item They are removed from simulation
\end{itemize}
\item For each midwife with information to share
\begin{itemize}
\item With probability p, their memory of games with the referred woman is shared
\item The memory is no longer eligible to be shared
\end{itemize}
\end{itemize}
\end{itemize}
